\section{Evaluation}
\label{sec:eval}

We have finished the code. But it is still being tested. We are going
to perform experiments to evaluate our system in the near future.

To evaluate our work, experiments will be performed on multi-disks
systems with and without our green target. Performance results of
power consumption and IO speed will be compared. To prove that the
green target can save energy, system using green target should report
significant less power consumption and comparative IO speed than
system with same experiment setup but not using the green target.
Power consumption can be measured using watt-meter connected to
machine and disks; IO performance can be measured using Filebench in
unit of ops/sec. To make the comparison fair, we trace block IO of
workloads beforehand and replay the traces on the two systems. 

The experiments will be performed under different configuration
combinations. The first configuration option is workload. Because
different workloads can exhibit very different IO characteristics, the
comparison will be performed per workload. We will start with a simple
workload, file compression, then extend to file server with large
files. Workloads should be large so that most physical disks will be
covered. 

The second configuration option is file system. File systems with
different features such as journalling and allocation policy will
behave differently on block IO. We are going to consider Ext2 and
Ext3. 

The third configuration option is IO scheduler. IO scheduler
determines how IO requests are grouped and issued. It might has great
impact on the effectiveness of the green target. We plan to consider
Anticipatory and Noop Scheduler in our experiment. 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% For Emacs:
% Local variables:
% fill-column: 70
% End:
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% For Vim:
% vim:textwidth=70
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% LocalWords:  
