\section{Related Work} 
\label{sec:related} 

Our study provides a multi-disk (hybrid) system in the purpose of
saving energy. To achieve that, we use energy-efficient disk as cache
and perform data migration and grouping using information obtained
from traces study. We discuss related work that covers the following
aspects: save energy, hybrid disk, data grouping and workload trace
study.

\textbf{Save Energy}. Energy efficiency of storage systems is an
interesting problem that is being actively researched. Sehgal et al.
\cite{fast10fsgreen} studied the power consumption of servers when
different workloads are running. Kothiyal et al.
\cite{systor09greencomp} presented empirical analysis of how lossless
compression influences power consumption of servers. Li et al.
\cite{fast12emc-energy} presented the first study of power consumption
of really running enterprise-scale backup systems. A category of
methods to save energy is using data replication to decrease either
disk head movement \cite{huangfs2, pred_data_grouping} or the number
of active disks being used \cite{Weddle07paraid}. 

\textbf{Hybrid disk}. There are various studies of hybrid disk,
wherein SSDs were used as cache disks \cite{Bisson07ahybrid,
Debnath_SkimpyStash, Debnath_Bloomflash, flashcache_experiments}.
Among them, few of them was really focusing on the energy efficiency
aspect of hybrid disk\cite{Bisson07ahybrid}. Although Zhu et al.
\cite{Zhu04reducingenergy} was also studying power aware cache, their
cache was in volatile RAM instead of non-volatile disk. Carrera et al.
\cite{slow_fast} presented a hybrid storage system that combines low
and high speed disks to save energy.

\textbf{Data grouping}. Wildani et al. \cite{Wildani_grouping}
presented data grouping of working set, however, their work only
contained analysis of offline traces. It was not implemented or
experimented on real system. The Energy-Efficient File System (EEFS)
groups files with high temporal access locality
\cite{Li06highperformance}. Essary et al. \cite{pred_data_grouping}
also performed predictive data grouping to reduce head movements for
saving energy.  Pinheiro and Bianchini \cite{migration04} used the
fact that regularly only a small subset of data is accessed by a
system, and migrated frequently accessed data to a small number of
active disks, keeping the remaining disks off, which is a kind of data
grouping.

\textbf{Trace study}. Trace extraction is a popular method used by
system researchers to analyze the system behavior. The analysis can be
used to optimize several important features of the system like CPU and
memory utilization, I/O throughput, latency, etc. Several reseachers
have used trace analysis to find correlations between disk block
accesses. Z. Li et al \cite{Li04c-miner} used data mining techniques
to find block correlations. T. Li et al \cite{Li_model} used block
traces to to run-time modeling to estimate the power consumption of
servers. Douglas et al. \cite{Douglis_95} used efficient algorithms
based on machine learning techniques on block traces to spin down
disks and extend battery life in mobile computers. V. Torasov
\cite{fast12t2m} used trace analysis to evaluate performance and
energy efficiency in file system server workloads extensions.


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% For Emacs:
% Local variables:
% fill-column: 70
% End:
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% For Vim:
% vim:textwidth=70
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% LocalWords:  SMR HDDs drive's SMRs
